---
title: "exploring"
author: "Janek Teders"
date: "December 8, 2018"
output: pdf_document
---

```{r}
dat <- read.csv("kc_house_data.csv", stringsAsFactors = F)
str(dat)
hist(dat$price, breaks = "FD")
median(dat$price)
quantile(dat$price, seq(0, 1, 0.01))
nrow(dat)
```

We want to keep date, price, bedrooms, bathrooms, sqft_living, sqft_lot, floors, waterfront, yr_built, yr_renovated, longitude, sqft_living15, sqft_lot15

might remove: sqft_above, sqft_basement, grade

remove view, condition, zip, latitude (because of shittiness)

conversion: convert sqfeet into sqm (1 sqft = 0.092903 sqm) for every var. done.
            date: (needs reformating, try with week and month) done.
            yr_renovated: try as bool for "recently renovated (no more than 5 or 10 years             ago)" or renovated at all (bool) done.
            
clean up: maybe negative, zeros
```{r}
any(is.na(dat))
```


Attack plan:

- outliers (too high, too low)
- distr. plot for variables, pick interesting ones
- outliers detection (cooks dist., leverage etc.) and annihilation
- correlation between variables and response var and transformation
- compare full and reduced models, F-statistics

Covert sqft into sqm:
```{r}
dat[,c("sqm_living",
       "sqm_lot",
       "sqm_above",
       "sqm_basement",
       "sqm_living15",
       "sqm_lot15")] <- dat[, c("sqft_living", 
                                "sqft_lot",
                                "sqft_above",
                                "sqft_basement", 
                                "sqft_living15",
                                "sqft_lot15")]  * 0.092903

dat <- dat[, -which(names(dat) %in% c("sqft_living", "sqft_lot", "sqft_above",
               "sqft_basement", 
               "sqft_living15",
               "sqft_lot15"))]
str(dat)
```

Change date format by adding a month of year and a week of year column:
```{r}
library(tidyverse)
#install.packages("lubridate")
library(lubridate)

full_date_column <- dat$week_of_year <- substr(dat$date, 1, 8) %>%
  ymd %>%
  as.Date

dat$week_of_year <- format(full_date_column, "%W")
dat$month_of_year <- format(full_date_column, "%m")
str(dat)
```

Variable: yr_renovated
comparisons of different house price means for different renovation intervals.
```{r}
paste("percentage renovated houses = ", round(length(dat$yr_renovated[dat$yr_renovated > 0])/nrow(dat), 3) * 100, "%") 

a <- mean(dat$price[dat$yr_renovated > 0])
b <- mean(dat$price[dat$yr_renovated == 0])
c <- mean(dat$price)
rbind("mean price of renov. houses" = a,
  "mean price of non renov. houses " = b,
  "mean price of all houses" = c)

mean(dat$price[dat$yr_renovated > 0 & dat$yr_renovated <= 2000])
mean(dat$price[dat$yr_renovated > 2000])
```

Create a new bool variable for a house being renovated at some point or not.
```{r}
dat$renovated <- ifelse(dat$yr_renovated > 0, 1, 0)
str(dat)
```

