---
title: "exploring"
author: "Janek Teders"
date: "December 8, 2018"
output: pdf_document
---

```{r}
dat <- read.csv("kc_house_data.csv", stringsAsFactors = F)
str(dat)
hist(dat$price, breaks = "FD")
median(dat$price)
quantile(dat$price, seq(0, 1, 0.01))
nrow(dat)
```

We want to keep date, price, bedrooms, bathrooms, sqft_living, sqft_lot, floors, waterfront, yr_built, yr_renovated, longitude, sqft_living15, sqft_lot15

might remove: sqft_above, sqft_basement, grade

remove view, condition, zip, latitude (because of shittiness)

conversion: convert sqfeet into sqm (1 sqft = 0.092903 sqm) for every var.
            date: (needs reformating, try with week and month)
            yr_renovated: try as bool for "recently renovated (no more than 5 or 10 years             ago)" or renovated at all (bool)
            
clean up: look for NA's, maybe negative, zeros, outliers (too high, too low)

Attack plan:

- distr. plot for variables, pick interesting ones
- outliers detection (cooks dist., leverage etc.) and annihilation
- correlation between variables and response var and transformation
- compare full and reduced models, F-statistics
- 

```{r}
hist(dat$yr_renovated, breaks = "FD")
sort(unique(dat$yr_renovated))
```

              
              
```{r}
lmo <- lm(price ~. ,data = dat[,-2])
summary(lmo)
```

```{r}
hist(dat$sqft_basement * 0.092903, breaks = "FD")
```

