---
title: "Exploring"
author: "Nicolas Carmona, Niklas Tillenburg, Janek Teders"
date: "December 8, 2018"
output: pdf_document
---

```{r include=FALSE}
library(tidyverse)
```

## Attack plan:

- outliers (too high, too low)
- distr. plot for variables, pick interesting ones
- outliers detection (cooks dist., leverage etc.) and annihilation
- correlation between variables and response var and transformation
- compare full and reduced models, F-statistics

## Reading in the dataset
```{r}
dat <- read.csv("kc_house_data.csv", stringsAsFactors = F)
str(dat)
```

\newpage

## Which variables to keep, which not

keep: 

- date, price
- bedrooms
- bathrooms
- sqft_living
- sqft_lot
- floors
- waterfront
- yr_built
- yr_renovated
- longitude
- sqft_living15
- sqft_lot15

might remove: 

- sqft_above
- sqft_basement
- grade
- id(?)

remove:

- view
- condition
- zip
- latitude (because of shittiness)

conversion: 

* convert sqfeet into sqm (1 sqft = 0.092903 sqm) for every var. done.
* date: (needs reformating, try with week and month) done.
* yr_renovated: try as bool for "recently renovated (no more than 5 or 10 years             ago)" or renovated at all (bool) done.

## Clean up for further processing

clean up: maybe negative, zeros

### Check for NA's, unreasonably negative values and inspect zeros:
```{r}
any(is.na(dat))
```


### Convert sqft into sqm:
```{r}
sqft_columns <- grepl("sqft", colnames(dat)) %>% colnames(dat)[.]

sqm_columns <- gsub("sqft", "sqm", sqft_columns)

dat[, sqm_columns] <- dat[, sqft_columns]  * 0.092903

dat <- -which(names(dat) %in% sqft_columns) %>% dat[,.]
str(dat)
```

### Adding a month of year and a week of year column, remove date:
```{r include=FALSE}
#install.packages("lubridate")
library(lubridate)
```

```{R}
full_date_column <- substr(dat$date, 1, 8) %>% ymd %>% as.Date

dat$week_of_year <- format(full_date_column, "%W")
dat$month_of_year <- format(full_date_column, "%m")
dat <- -which(names(dat) %in% "date") %>% dat[,.]
str(dat)
```

### Variable: yr_renovated

comparisons of different house price means for different renovation intervals.
```{r}
rbind(
  "percentage renovated houses" = 
    round(length(dat$yr_renovated[dat$yr_renovated > 0])/nrow(dat), 3) * 100,
  "mean price of all houses" = 
    mean(dat$price),
  "mean price of renov. houses" = 
    mean(dat$price[dat$yr_renovated > 0]),
  "mean price of non renov. houses" =
    mean(dat$price[dat$yr_renovated == 0]),
  "mean price of renov. houses before 2000" = 
    mean(dat$price[dat$yr_renovated > 0 & dat$yr_renovated <= 2000]),
  "mean price of houses renov. after 2000" = 
    mean(dat$price[dat$yr_renovated > 2000]))
```

Create a new factor variable for a house being renovated at some point or not.
```{r}
dat$renovated <- as.factor(ifelse(dat$yr_renovated > 0, "yes", "no"))
str(dat)
```

```{r}
neat_dat <- select(dat, -lat, -condition, -view, -zipcode, -id) %>%
  select(price:long, week_of_year, month_of_year, renovated, sqm_living:sqm_lot15)
str(neat_dat)
```

