---
title: "Storytelling"
author: "Janek Teders"
date: "December 14, 2018"
output: pdf_document
---

```{r, setup}
library(tidyverse)
library(lubridate)
library(car)

dat <- read_csv("kc_house_data.csv")

dat_1 <- dat %>%
  mutate_at(
    vars(starts_with("sqft")),
    function(x) x * 0.092903
  ) %>%
  rename_at(
    vars(starts_with("sqft")),
    function(x) str_replace(x, "sqft", "sqm")
  ) %>%
  mutate(
    week_of_year = week(date),
    month_of_year = month(date),
    renovated = factor(ifelse(yr_renovated > 0, "yes", "no"))
  ) %>%
  select(-starts_with("sqm"), starts_with("sqm"))
```

# Chapter 1: Variable selection

- remove variables based on correlation
- new variable: mean house price per zipcode

```{r}
set.seed(1234)
full_dat<- dat_1 %>%
  sample_n(nrow(.))

first_fifth_avg <- full_dat %>%
  slice(1:(n()/5)) %>%
  group_by(zipcode) %>%
  summarise(mean_price_zip = mean(price))

result <- full_dat %>%
  slice((n()/5):n()) %>%
  left_join(., first_fifth_avg, key = zipcode) %>%
  select(zipcode, mean_price_zip, price) 

(cor(result$price, result$mean_price_zip))

dat_2 <- dat_1 %>%
  left_join(., first_fifth_avg, key = zipcode)
```




```{r}
(corrs <- dat_2 %>%
  select(-renovated, -date, -id) %>%
  cor(.) %>%
  .[,1] %>%
  abs(.) %>%
  sort(.) %>%
  as.matrix(., nrow(length(.))))

good_corr <- corrs %>%
  rownames(.) %>%
  .[10:length(.)]
```

- Did a cut after yr_renovated, correlation jumps from 0.12 to 0.25 at this point.
- checking if we keep sqm_living or sqm_above and sqm_basement, because they consist of each other.

```{r}
lmo_1 <- dat_2 %>%
  select(one_of(good_corr), renovated) %>%
  lm(data = ., log10(price) ~ .)

lmo_2 <- dat_2 %>%
  select(one_of(good_corr), renovated, -sqm_living) %>%
  lm(data = ., log10(price) ~ .)

lmo_3 <- dat_2 %>%
  select(one_of(good_corr), renovated, -sqm_above, -sqm_basement) %>%
  lm(data = ., log10(price) ~ .)


test <- list(lmo_1, lmo_2, lmo_3)
sapply(test, function(x) summary(x)$adj.r.squared)


anova(lmo_2, lmo_3)
```

- cool thing: na's in sqm_living because it is a linear combination of sqm_above and sqm_basement
- lmo_3 (with sqm_living) performs better than lmo_2 (with sqm_above and sqm_basement)

```{r}
vars_1 <- good_corr[! good_corr %in% c("sqm_above", "sqm_basement")]
dat_3 <- dat_2 %>%
  select(one_of(vars_1), renovated) %>%
  mutate(waterfront = factor(waterfront, labels = c("no", "yes")))

write_csv(dat_3, "dat_3.csv")
```
















