---
title: "vars_finalized"
author: "Janek Teders"
date: "December 16, 2018"
output: pdf_document
---

```{r}
library(MASS)
library(tidyverse)
library(lubridate)
library(car)
library(magrittr)
library(faraway)
library(leaps)

dat_3 <- read_csv("dat_3.csv") %>%
  mutate(
    renovated = as.factor(renovated),
    waterfront = as.factor(waterfront),
    price = log10(price)
  )
```

# Janeks suggestions concerning florrs, bedrooms and lat

- According to the BIC we're going to choose the log10 transformation of floors.
- We'll use the log10 transformation as well on the lat variable (BIC)
- Removing the rows with 0 bedrooms (13), because it seems unlikely and slightly improves the model and removing the house with 33 bedrooms, as this seems to be a typing error and drastically improves the model due to its huge leverage.
- We will use the sqrt transformation of the bedrooms (BIC)
```{r}
dat_4 <- dat_3 %>%
  filter(
    bedrooms != 0 & bedrooms != 33
  ) %>%
  mutate(
    floors = log10(floors),
    bedrooms = sqrt(bedrooms)
  )
```

# Nicolas suggestions concerning view, bathrooms and sqm_living15

- add new variable wasViewed and keep view as it is (BIC)
- bathrooms to the power of 1/5 according to best BIC
- sqm_living15?

```{r}
dat_5 <- dat_4 %>%
  mutate(
    wasViewed = factor(ifelse(view > 0, 1, 0)),
    bathrooms = bathrooms^(1/5)
  )
```

# Niklas suggestions concerning 

- log10 of mean_price_zip (BIC)
- log10 of grade (BIC)
- sqrt of sqm_living (BIC)

```{r}
dat_6 <- dat_5 %>%
  mutate(
    mean_price_zip = log10(mean_price_zip),
    grade = log10(grade),
    sqm_living = sqrt(sqm_living)
  )
```

# Final comparison

```{r}
old_dat <- read_csv("kc_house_data.csv") %>%
  filter(
    bedrooms != 0 & bedrooms != 33
  ) %>%
  mutate_at(
    vars(starts_with("sqft")),
    function(x) x * 0.092903
  ) %>%
  rename_at(
    vars(starts_with("sqft")),
    function(x) str_replace(x, "sqft", "sqm")
  ) %>%
  mutate(
    week_of_year = week(date),
    month_of_year = month(date),
    renovated = factor(ifelse(yr_renovated > 0, "yes", "no")),
    waterfront = as.factor(waterfront),
    wasViewed = factor(ifelse(view > 0, 1, 0)),
    price = log10(price)
  ) %>%
  select(-starts_with("sqm"), -date, -id, starts_with("sqm"))

pre_selection_model <- old_dat %>%
  lm(data = ., price ~ .)

old_model <- dat_3 %>%
  lm(data = ., price ~ .)

trans_model <- dat_6 %>%
  lm(data = ., price ~ .)


summary(pre_selection_model)
BIC(pre_selection_model, old_model, trans_model)
#anova(pre_selection_model, old_model, trans_model)

nrow(old_dat)
nrow(dat_6)
nrow(dat_3)
```

# k-fold validation
## 5
```{r}
install.packages("disdat")
library(disdat)
k <- 5
kFold
```

